% 17D heuristic variants
\footnotesize
\begin{longtabu} to \columnwidth {X[.6,l]X[.65,l]X[.75,l]X[p]X[l]}
	\caption[Published clinical and nonclinical data comparing the 17D substrains.]{Published clinical and nonclinical data comparing the 17D substrains.\label{substrain_comparison_Trials}}\\
	\rowfont[1]{\bfseries}
	\toprule
	Trial Type and Reference & Cohort & Endpoints  & Strain\newline (Substrain,\newline National Origin) & Results    \\ \midrule
	Nonclinical\tnote{a}                     & Cynomolgous Macaques                 & Viremia (Viscerotropism), Immunogenicity & 1.168-73\newline(17D-213, WHO Reference Strain)\newline 2.17D-204 Secondary Seed, UK\newline 3.17D-204 Secondary Seed, Senegal & 1.All groups of equivalent immunogenicity.\newline 2.Greater viremias observed for group receiving 168-73.\newline 3.Lower histological scores for group receiving 168-73.                                                                                                                            \\
Clinical\tnote{b}                           & Healthy Adults (n=211)               & Immunogenicity, adverse reactions        & 1.Stamaril\textsuperscript{\textregistered}\newline(17D-204, France)\newline 2.Arilvax\textsuperscript{\textregistered}\newline(17D-204, UK)                                                        & 1.Similar rates of adverse reactions and seroconversion for both vaccines.\newline 2.Higher immunogenicity for group receiving Stamaril\textsuperscript{\textregistered}.                                                                                                                                                      \\

Clinical\tnote{c}                 & Children, 9mos.-10yrs. (n=1,107)     & Immunogenicity, Adverse reactions        & 1.YF-Vax\textsuperscript{\textregistered}\newline(17D-204, USA)\newline 2.Arilvax\textsuperscript{\textregistered}\newline(17D-204, UK)                                                            & 1.Greater seroconversion rates for Arilvax\textsuperscript{\textregistered}.\newline 2.Similar rates of adverse events.\newline 3.Similar immunogenicity for both vaccines.                                                                                                                                                          \\

Clinical\tnote{d} & Healthy Adults (n=1087)              & Immunogenicity, Adverse Reactions        & 1.17D-WHO\newline(17D-213, Brazil)\newline 2.17DD\/013Z\newline(17DD, Brazil)\newline 3.17DD\/102\/84\newline(17DD, Brazil)                          & 1.Greater immunogenicity for 17D-213 substrain vaccine.\newline 2.Similar rates of serovonversion for all vaccines considered. 3. Slightly higher rates of minor adverse reactions and detectable viremia for 17D-213 substrain.                                                               \\
Clinical\tnote{e}                       & Healthy Adults (n=304)               & Immunogenicity, Adverse Reactions        & 1.Stamaril\textsuperscript{\textregistered}\newline(17D-204, France)\newline 2.RKI-YF\textsuperscript{\textregistered}\newline(17D-213, Germany)\newline 3.Berna-YF\textsuperscript{\textregistered}\newline(17D-213, Netherlands)                 & 1.All groups immunogenic (GMT \textgreater1:10).\newline 2.Higher ab titers for males receiving 17D-213 substrain products.\newline 3.No difference in immunogenicities between 17D-213 products administered.\newline 4.Higher rate of injection site erythema and pain for RKI-YF\textsuperscript{\textregistered}, compared to Berna-YF\textsuperscript{\textregistered}. \\
	
	
Clinical\tnote{f}                       & Healthy Adults and Children (n=2514) & Adverse Reactions                        & 1.17DD/Fiocruz\newline(17DD, Brazil)\newline 2.Stamaril\textsuperscript{\textregistered}\newline(17D-204, France)                                                   & No significant differences in rates of local or systemic adverse events.                                                                                                                                                                                                                 \\ \bottomrule
	
	
		\bottomrule
\end{longtabu}

